---
title: "Report on a study on medication non-adherence"
author: "Ana, Sophie, Giando and Geraldine"
date: "2025-06-05"
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: "Table of Contents"
    number-sections: true
    code-fold: true
---

# Introduction
A survey was conducted to understand the extent of medication non-adherence in four languages: Italian, Portuguese, French and English. 

# Data collection
The survey was conducted online via Google Forms and the data was collected in spreadsheets for analysis.

# Data cleaning
The data was cleaned using R and the following steps were taken: patients who responded that they adhere to their treatment were excluded from the analysis of causes of non-adherence. All other replies were included as reported.

# Results
## Adherence
The results show that the majority of patients responding to this survey do adhere to their treatment as prescribed by their doctor. Overall, `r nonadh_n` (`r nonadh_p`%) of patients do not adhere to their treatment.

```{r data-grab}
source("scripts/grab.R")
n <- nrow(all_data)
nonadh_n <- sum(all_data$medication_adherence!="I always take them as the doctor told me")
nonadh_p <- round(nonadh_n/n*100, 2)
```



## Causes of non-adherence
The main causes of non-adherence were:
- Forgetfulness
- Lack of time
- Lack of money
- Lack of support


```{r}
source("scripts/intervention_plot.R")
```