---
title: "Report on a study on medication non-adherence"
author: "Ana, Sophie, Giando and Geraldine"
date: "2025-06-05"
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: "Table of Contents"
    number-sections: true
    code-fold: true
execute: 
  echo: false
  message: false
  warning: false
  error: true
  output: true
  cache: false
---

# Introduction

A survey was conducted to understand the extent of medication non-adherence in four languages: Italian, Portuguese, French and English.

# Data collection

The survey was conducted online via Google Forms and the data was collected in spreadsheets for analysis.

# Data cleaning

The data was cleaned using R and the following steps were taken: patients who responded that they adhere to their treatment were excluded from the analysis of causes of non-adherence. All other replies were included as reported.

# Results

## Adherence

```{r data-grab}
options(digits=1)
library(knitr)
source("scripts/grab.R")
n <- nrow(all_data)
nonadh_n <- sum(all_data$medication_adherence!="I always take them as the doctor told me")
nonadh_p <- round(nonadh_n/n*100, 2)
```

The results show that the majority of patients responding to this survey do adhere to their treatment as prescribed by their doctor. Overall, **n = `r nonadh_n` (`r nonadh_p`%)** of patients stated not adhering to their treatment as intended or prescribed.

```{r}
source("scripts/adherence-plot.R")
adherence_plot
```

```{r adherence-lang}
kable(adherence_by_country[order(adherence_by_country$n_total, decreasing = TRUE), ], caption = "Adherence by country", align = "c", col.names = c("Country", "Respondents (n)", "Adherent (n)", "Adherent (%)"))
```

```{r}
library(knitr)
kable(summary_stats, caption = "Summary of survey responses by language", align = "c", 
col.names = c("Language", "Respondents (n)", "Adherent (%)", "Sometimes forget (< once a week) (%)", "Sometimes forget (>  once a week) (%)", "Stopped (%))", "Impact on identity (%)", "Vouchers rating", "Fine rating", "Support program rating", "Phone reminders rating", "Emoji rating", "Pension collection rating", "Health info rating"))
```

```{r}
library(knitr)
summary_stats |> 
kable(caption = "Summary of survey responses by language", align = "c", 
col.names = c("Language", "Respondents (n)", "Adherent (%)", "Sometimes forget (< once a week) (%)", "Sometimes forget (>  once a week) (%)", "Stopped (%))", "Impact on identity (%)", "Vouchers rating", "Fine rating", "Support program rating", "Phone reminders rating", "Emoji rating", "Pension collection rating", "Health info rating"))
```

## Causes of non-adherence

The main causes of non-adherence were:

```{r}
source("scripts/causes.R")

# Category donut chart (if created in the script)
category_donut

# Reasons per patient bar chart (if created in the script)
reasons_per_patient

# If you want to see all plots in a grid (optional)
library(gridExtra)
grid.arrange(causes_plot, category_donut, ncol = 2)
```

```{r}
source("scripts/intervention_plot.R")
```

```{r}
source("scripts/word-bubbles.R")


```